A general framework for learning planning action models

### 2018-06-18 doc/aij18/background.tex
updates added to learning section

@@

A {\em classical planning frame} is a tuple $\Phi=\tup{F,A}$, where $F$ is a set of fluents and $A$ is a set of actions. An action $a\in A$ is defined with:

%{\em preconditions}, $\pre(a)\subseteq\mathcal{L}(F)$, {\em negative effects} $\eff^-(a)\subseteq\mathcal{L}(F)$ and {\em positive effects}, $\eff^+(a)\subseteq\mathcal{L}(F)$.

\begin{itemize}
\item $\pre(a)\in\mathcal{L}(F)$, the {\em preconditions} of $a$, is the set of literals that must hold for the action $a\in A$ to be applicable.
\item $\eff^+(a)\in\mathcal{L}(F)$, the {\em positive effects} of $a$, is the set of literals that are true after the application of the action $a\in A$.
\item $\eff^-(a)\in\mathcal{L}(F)$, the {\em negative effects} of $a$, is the set of literals that are false after the application of the action.
\end{itemize}

We say that an action $a\in A$ is {\em applicable} in a state $s$ iff $\pre(a)\subseteq s$. The result of applying $a$ in $s$ is the {\em successor state} denoted by $\theta(s,a)=\{s\setminus\eff^-(a))\cup\eff^+(a)\}$.

>>>>

Like in PDDL, we assume that fluents $F$ are instantiated from a set of {\em predicates} $\Psi$. Each predicate $p\in\Psi$ has an argument list of arity $ar(p)$. Given a set of {\em objects} $\Omega$, the set of fluents $F$ is induced by assigning objects in $\Omega$ to the arguments of predicates in $\Psi$, i.e.~$F=\{p(\omega):p\in\Psi,\omega\in\Omega^{ar(p)}\}$ s.t. $\Omega^k$ is the $k$-th Cartesian power of $\Omega$.

@@

A {\em classical planning frame} is a tuple $\Phi=\tup{F,A}$, where $F$ is a set of fluents and $A$ is a set of actions. An action $a\in A$ is defined with:
\begin{itemize}
\item $\pre(a)\in\mathcal{L}(F)$, the {\em preconditions} of $a$, is the set of literals that must hold for the action $a\in A$ to be applicable.
\item $\eff^+(a)\in\mathcal{L}(F)$, the {\em positive effects} of $a$, is the set of literals that are true after the application of the action $a\in A$.
\item $\eff^-(a)\in\mathcal{L}(F)$, the {\em negative effects} of $a$, is the set of literals that are false after the application of the action.
\end{itemize}
We assume that $\eff^-(a)\subseteq \pre(a)$, $\eff^-(a)\cap \eff^+(a)=\emptyset$ and $\pre(a)\cap \eff^+(a)=\emptyset$ and that actions $a\in A$ are instantiated from given action schemas. We say that an action $a\in A$ is {\em applicable} in a state $s$ iff $\pre(a)\subseteq s$. The result of applying $a$ in $s$ is the {\em successor state} denoted by $\theta(s,a)=\{s\setminus\eff^-(a))\cup\eff^+(a)\}$.
